### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsubsection{Noiseless Lossless Channel}
The channel of the system is noiseless and lossless if

\begin{equation} \label{eq:1}
  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
\end{equation}
$|K|$ represents the number of symbols in $K$.

Figure~\ref{fig:channel}a shows the example of the type of the channel. Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$. As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).

@@

Figure~\ref{fig:channel}b  shows the example of the type of the channel. Once the input symbol is determined, the output symbol is also determine. As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).

>>>>

\subsubsection{Noiseless Lossless Channel}
An information channel is noiseless and lossless if

\begin{equation} \label{chapter5:eq4}
  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
\end{equation}
$|K|$ represents the number of symbols in $K$.

Figure~\ref{fig:channel}(a) shows an example of the type of the channel. Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$. As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).

@@

Figure~\ref{fig:channel}(b) shows the example of the type of the channel. Once the input symbol is determined, the output symbol is also determine. As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
